The SMT Competition 2015--2018

### 2019-03-16 2018/report/table-winners-main-new.tex
Beautify layout of main track winners table.

\begin{tabular}{r@{\hskip 3em}c@{\hskip 2em}c@{\hskip 2em}c@{\hskip 2em}c}

@@

@@

ABVFP        &                 &                 &                        & {CVC4}                \\
ALIA         & {{[}Z3{]}}      & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
AUFBVDTLIA   &                 &                 & {CVC4}                 & {CVC4}                \\
AUFDTLIA     &                 &                 & {CVC4}                 & {CVC4}                \\
AUFLIA       & {CVC4}          & {CVC4}          & {CVC4}                 & {CVC4}                \\
AUFLIRA      & {{[}Z3{]}}      & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
AUFNIRA      & {CVC4}          & {Vampire}       & {Vampire}              & {CVC4}                \\
BV           & {{[}Z3{]}}      & {Q3B}           & {{[}Z3{]}}             & {CVC4}                \\
BVFP         &                 &                 &                        & {CVC4}                \\
FP           &                 &                 &                        & {CVC4}                \\
LIA          & {CVC4}          & {CVC4}          & {{[}Z3{]}}             & {{[}Z3{]}}            \\
LRA          & {CVC4}          & {CVC4}          & {{[}Z3{]}}             & {{[}Z3{]}}            \\
NIA          & {{[}Z3{]}}      & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
NRA          & {CVC4}          & {Vampire}       & {Redlog}               & {{[}Z3{]}/Vampire}    \\
QF\_ABV      & {Boolector}     & {Boolector}     & {Boolector}            & {Boolector}           \\
QF\_ABVFP    &                 &                 & {---}                  & {CVC4}                \\
QF\_ALIA     & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
QF\_ANIA     & {{[}Z3{]}}      & {CVC4}          & {CVC4}                 & {{[}Z3{]}}            \\
QF\_AUFBV    & {{[}MathSAT{]}} & {{[}MathSAT{]}} & {{[}MathSAT{]}}        & {CVC4}                \\
QF\_AUFLIA   & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
QF\_AUFNIA   & {CVC4}          & {CVC4}          & {{[}Z3{]}}             & {{[}Z3{]}}            \\
QF\_AX       & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
QF\_BV       & {Boolector}     & {Boolector}     & {Boolector/MinkeyRink} & {Boolector/MinkeyRink}\\
QF\_BVFP     & {Z3}            & {{[}Z3{]}}      & {{[}Z3{]}}             & {CVC4}                \\
QF\_DT       &                 &                 & {CVC4}                 & {CVC4}                \\
QF\_FP       & {Z3}            & {{[}MathSAT{]}} & {{[}Z3{]}}             & {COLIBRI}             \\
QF\_IDL      & {{[}Z3{]}}      & {{[}Z3{]}}      & {Yices2}               & {Yices2}              \\
QF\_LIA      & {{[}MathSAT{]}} & {{[}MathSAT{]}} & {{[}MathSAT{]}}        & {SPASS-SATT}          \\
QF\_LIRA     & {Yices2}        & {Yices2}        & {{[}Z3{]}}             & {{[}Z3{]}}            \\
QF\_LRA      &  {CVC4}         & {CVC4}          & {CVC4}                 & {CVC4}                \\
QF\_NIA      & {{[}Z3{]}}      & {{[}Z3{]}}      & {CVC4}                 & {CVC4}                \\
QF\_NIRA     & {CVC4}          & {CVC4}          & {SMT-RAT}              & {SMT-RAT}             \\
QF\_NRA      & {{[}Z3{]}}      & {{[}Z3{]}}      & {Yices2}               & {{[}Z3{]}}            \\
QF\_RDL      & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
QF\_SLIA     &                 &                 &                        & {CVC4}                \\
QF\_UF       & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
QF\_UFBV     & {Boolector}     & {Boolector}     & {Boolector}            & {Boolector}           \\
QF\_UFIDL    & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
QF\_UFLIA    & {{[}Z3{]}}      & {{[}Z3{]}}      & {Yices2}               & {Yices2}              \\
QF\_UFLRA    & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
QF\_UFNIA    & {CVC4}          & {Yices2/CVC4}   & {Yices2}               & {Yices2}              \\
QF\_UFNRA    & {{[}Z3{]}}      & {Yices2}        & {{[}Z3{]}}             & {Yices2}              \\
UF           & {CVC4}          & {CVC4}          & {Vampire}              & {CVC4/Vampire}        \\
UFBV         & {{[}Z3{]}}      & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
UFDT         &                 &                 & {CVC4}                 & {CVC4}                \\
UFDTLIA      &                 &                 & {Vampire}              & {CVC4}                \\
UFIDL        & {{[}Z3{]}}      & {CVC4}          & {CVC4}                 & {{[}Z3{]}}            \\
UFLIA        & {CVC4}          & {CVC4}          & {CVC4}                 & {CVC4}                \\
UFLRA        & {CVC3}          & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
UFNIA        & {CVC4}          & {Vampire}       & {Vampire}              & {{[}Z3{]}/Vampire}    \\

>>>>

  \begin{tabular}{r@{\hskip 3em}>{\columncolor[gray]{.95}[.5em][1em]}c@{\hskip 2em}>{\columncolor[gray]{.95}[1em][1em]}c@{\hskip 2em}>{\columncolor[gray]{.95}[1em][1em]}c@{\hskip 2em}>{\columncolor[gray]{.95}[1em][0.5em]}c}

@@

\rc

@@

\cc ABVFP        & \cc             & \cc             & \cc                    & \cc {CVC4}            \\
\cc ALIA         & {{[}Z3{]}}      & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
\drc
\cc AUFBVDTLIA   & \cc             & \cc             & {CVC4}                 & {CVC4}                \\
\cc AUFDTLIA     & \cc             & \cc             & {CVC4}                 & {CVC4}                \\
\drc
\cc AUFLIA       & {CVC4}          & {CVC4}          & {CVC4}                 & {CVC4}                \\
\cc AUFLIRA      & {{[}Z3{]}}      & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
\drc
\cc AUFNIRA      & \cc {CVC4}      & {Vampire}       & {Vampire}              &\cc  {CVC4}            \\
\rc
\cc BV           &  {{[}Z3{]}}     & {Q3B}           & {{[}Z3{]}}             &  {CVC4}               \\
\cc BVFP         & \cc             & \cc             & \cc                    & \cc {CVC4}            \\
\cc FP           & \cc             & \cc             & \cc                    & \cc {CVC4}            \\
\cc LIA          & \dcc {CVC4}     & \dcc{CVC4}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
\cc LRA          & {CVC4}          & {CVC4}          & \dcc {{[}Z3{]}}        & \dcc {{[}Z3{]}}       \\
\cc NIA          & {{[}Z3{]}}      & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
\rc
\cc NRA          & {CVC4}          & {Vampire}       & {Redlog}               & {{[}Z3{]}/Vampire}    \\
\cc QF\_ABV      & {Boolector}     & {Boolector}     & {Boolector}            & {Boolector}           \\
\cc QF\_ABVFP    & \cc             &  \cc            & \cc {---}              & \cc {CVC4}            \\
\cc QF\_ALIA     & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
\drc
\cc QF\_ANIA     & \cc {{[}Z3{]}}  & {CVC4}          & {CVC4}                 & {{[}Z3{]}}            \\
\cc QF\_AUFBV    & {{[}MathSAT{]}} & {{[}MathSAT{]}} & {{[}MathSAT{]}}        & \cc {CVC4}            \\
\drc
\cc QF\_AUFLIA   & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
\cc QF\_AUFNIA   & {CVC4}          & {CVC4}          & \dcc {{[}Z3{]}}        & \dcc {{[}Z3{]}}       \\
\cc QF\_AX       & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
\drc
\cc QF\_BV       & {Boolector}     & {Boolector}     & {Boolector/MinkeyRink} & {Boolector/MinkeyRink}\\
\cc QF\_BVFP     & {Z3}            & {{[}Z3{]}}      & {{[}Z3{]}}             & \cc {CVC4}            \\
\drc
\cc QF\_DT       & \cc             & \cc             & {CVC4}                 & {CVC4}                \\
\rc
\cc QF\_FP       & {Z3}            & {{[}MathSAT{]}} & {{[}Z3{]}}             & {COLIBRI}             \\
\cc QF\_IDL      & \dcc {{[}Z3{]}} & \dcc {{[}Z3{]}} & {Yices2}               & {Yices2}              \\
\cc QF\_LIA      & {{[}MathSAT{]}} & {{[}MathSAT{]}} & {{[}MathSAT{]}}        & \cc {SPASS-SATT}      \\
\cc QF\_LIRA     & {Yices2}        & {Yices2}        & \dcc {{[}Z3{]}}        & \dcc {{[}Z3{]}}       \\
\cc QF\_LRA      &  {CVC4}         & {CVC4}          & {CVC4}                 & {CVC4}                \\
\cc QF\_NIA      & {{[}Z3{]}}      & {{[}Z3{]}}      & {CVC4}                 & {CVC4}                \\
\cc QF\_NIRA     & {CVC4}          & {CVC4}          & {SMT-RAT}              & {SMT-RAT}             \\
\cc QF\_NRA      & \dcc {{[}Z3{]}} & \dcc {{[}Z3{]}}      & \cc {Yices2}      & \cc {{[}Z3{]}}        \\
\cc QF\_RDL      & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
\cc QF\_SLIA     & \cc             & \cc             & \cc                    & \cc {CVC4}            \\
\cc QF\_UF       & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
\drc
\cc QF\_UFBV     & {Boolector}     & {Boolector}     & {Boolector}            & {Boolector}           \\
\cc QF\_UFIDL    & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
\cc QF\_UFLIA    & \dcc {{[}Z3{]}} & \dcc {{[}Z3{]}} & {Yices2}               & {Yices2}              \\
\cc QF\_UFLRA    & {Yices2}        & {Yices2}        & {Yices2}               & {Yices2}              \\
\drc
\cc QF\_UFNIA    & \cc {CVC4}      & {Yices2/CVC4}   & {Yices2}               & {Yices2}              \\
\rc
\cc QF\_UFNRA    & {{[}Z3{]}}      & {Yices2}        & {{[}Z3{]}}             & {Yices2}              \\
\cc UF           & {CVC4}          & {CVC4}          & \dcc {Vampire}         & \dcc {CVC4/Vampire}   \\
\cc UFBV         & {{[}Z3{]}}      & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
\cc UFDT         & \cc             & \cc             & {CVC4}                 & {CVC4}                \\
\rc
\cc UFDTLIA      &                 &                 & {Vampire}              & {CVC4}                \\
\cc UFIDL        & \cc {{[}Z3{]}}  & {CVC4}          & {CVC4}                 & \cc {{[}Z3{]}}        \\
\drc
\cc UFLIA        & {CVC4}          & {CVC4}          & {CVC4}                 & {CVC4}                \\
\cc UFLRA        & \cc {CVC3}      & {{[}Z3{]}}      & {{[}Z3{]}}             & {{[}Z3{]}}            \\
\drc
\cc UFNIA        & \cc {CVC4}      & {Vampire}       & {Vampire}              & {{[}Z3{]}/Vampire}    \\
